---
title: "Homework2"
author: "Alisha Meena Gursahaney"
date: "2023-01-06"
output: html_document
---
#Question 1
Citations:

R Sequence function: https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/seq

R Replicate function: https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/rep

-used these citations because I felt that some of my methods differed from those taught in class and wanted to put them just in case

(a)
```{r}
rep("Q1", 4)
```

(b)
```{r}
seq(50.0, 100.0, by = 2.5)

```

(c)
```{r}
rep(2010:2017, each=4)
```

(d)
```{r}
vect<-rep(2010:2017, each=4)
vect[25:31]
```


(e)
```{r}
vec1<-seq(1295,1299)
vec2<-seq(1300,1290, by=-1)
c(vec1,vec2)
```

(f)
```{r}
seq(4160,3530, by=-105)
```

#Question 2
Set up dataframe and library for all question parts
```{r}
PVA_data<-read.csv("/Users/alishagursahaney/Desktop/R/PVA.csv")
library(dplyr)
```
(a)
```{r}
typeof(PVA_data$Age)
mean(PVA_data$Age)
```

(b)
```{r}
# 1st method
names(PVA_data)[5]<- "income_level"
names(PVA_data)[8]<- "current_gift"
head(PVA_data)
```
way to do this in one line of code:

names(PVA_data)[c(5,8)]<- c("income_level", "current_gift")


using dplyr:

PVA_data%>%
  
  rename(Income=income_level, Current.gift=current_gift)

(c)
```{r}
New_data<-PVA_data%>%
  filter(Age <= 60 & income_level >5)
head(New_data)
```
(d)
```{r}
Donors<-PVA_data%>%
  filter(current_gift > 50 & Time.Between.Gifts > 1)
mean(Donors$current_gift)
```

(e)
```{r}
PVA_data%>%
  summarise(max(Smallest.Gift), max(Largest.Gift), max(current_gift))
```

(f)
```{r}
# Income = 1
Income1<-PVA_data%>%
  filter(income_level == 1)
median(Income1$current_gift)

# Income = 2
Income2<-PVA_data%>%
  filter(income_level == 2)
median(Income2$current_gift)

# Income = 3
Income3<-PVA_data%>%
  filter(income_level == 3)
median(Income3$current_gift)

# Income = 4
Income4<-PVA_data%>%
  filter(income_level == 4)
median(Income4$current_gift)

# Income = 5
Income5<-PVA_data%>%
  filter(income_level == 5)
median(Income5$current_gift)

# Income = 6
Income6<-PVA_data%>%
  filter(income_level == 6)
median(Income6$current_gift)

# Income = 7
Income7<-PVA_data%>%
  filter(income_level == 7)
median(Income7$current_gift)
```

